\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-05-16 doc/paper.tex

\section{Speed test SLHA input file}
\label{sec:speed-test-slha-template-file}
%
\begin{lstlisting}
Block MODSEL                 # Select model
    6    0                   # flavour violation
    1    1                   # mSUGRA
Block SMINPUTS               # Standard Model inputs
    1   1.279180000e+02      # alpha^(-1) SM MSbar(MZ)
    2   1.166390000e-05      # G_Fermi
    3   1.189000000e-01      # alpha_s(MZ) SM MSbar
    4   9.118760000e+01      # MZ(pole)
    5   4.200000000e+00      # mb(mb) SM MSbar
    6   1.709000000e+02      # mtop(pole)
    7   1.777000000e+00      # mtau(pole)
Block SOFTSUSY               # SOFTSUSY specific inputs
    1   1.000000000e-04      # tolerance
    2   2                    # up-quark mixing (=1) or down (=2)
    3   0                    # printout
    5   1                    # 2-loop running
    7   2                    # EWSB and Higgs mass loop order
Block FlexibleSUSY
    0   1.000000000e-04      # precision goal
    1   0                    # max. iterations (0 = automatic)
    2   0                    # algorithm (0 = two_scale, 1 = lattice)
    3   0                    # calculate SM pole masses
    4   1                    # pole mass loop order
    5   1                    # EWSB loop order
Block SPhenoInput            # SPheno specific input
    1  -1                    # error level
    2   1                    # SPA conventions
    11  0                    # calculate branching ratios
    13  0                    # include 3-Body decays
    12  1.000E-04            # write only branching ratios larger than this value
    31  -1                   # fixed GUT scale (-1: dynamical GUT scale)
    32  0                    # Strict unification
    34  1.000E-04            # Precision of mass calculation
    35  40                   # Maximal number of iterations
    37  1                    # Set Yukawa scheme
    38  2                    # 1- or 2-Loop RGEs
    50  1                    # Majorana phases: use only positive masses
    51  0                    # Write Output in CKM basis
    52  0                    # Write spectrum in case of tachyonic states
    55  1                    # Calculate one loop masses
    57  0                    # Calculate low energy constraints
    60  0                    # Include possible, kinetic mixing
    65  1                    # Solution tadpole equation
    75  0                    # Write WHIZARD files
    76  0                    # Write HiggsBounds file
    86  0.                   # Maximal width to be counted as invisible in Higgs decays
    510 0.                   # Write tree level values for tadpole solutions
    515 0                    # Write parameter values at GUT scale
    520 0.                   # Write effective Higgs couplings (HiggsBounds blocks)
    525 0.                   # Write loop contributions to diphoton decay of Higgs
Block MINPAR
    1   [50..1000]           # m0(MX)
    2   [50..1000]           # m12(MX)
    3   [1..100]             # tan(beta)(MZ) DRbar
    4   {-1,+1}              # sign(mu)
    5   [-1000..1000]        # A0(MX)
\end{lstlisting}

>>>>

\section{Speed test SLHA input file}
\label{sec:speed-test-slha-template-file}
%
\begin{lstlisting}
Block MODSEL                 # Select model
    6    0                   # flavour violation
    1    1                   # mSUGRA
Block SMINPUTS               # Standard Model inputs
    1   1.279180000e+02      # alpha^(-1) SM MSbar(MZ)
    2   1.166390000e-05      # G_Fermi
    3   1.189000000e-01      # alpha_s(MZ) SM MSbar
    4   9.118760000e+01      # MZ(pole)
    5   4.200000000e+00      # mb(mb) SM MSbar
    6   1.709000000e+02      # mtop(pole)
    7   1.777000000e+00      # mtau(pole)
Block SOFTSUSY               # SOFTSUSY specific inputs
    1   1.000000000e-04      # tolerance
    2   2                    # up-quark mixing (=1) or down (=2)
    3   0                    # printout
    5   1                    # 2-loop running
    7   2                    # EWSB and Higgs mass loop order
Block FlexibleSUSY
    0   1.000000000e-04      # precision goal
    1   0                    # max. iterations (0 = automatic)
    2   0                    # algorithm (0 = two_scale, 1 = lattice)
    3   0                    # calculate SM pole masses
    4   2                    # pole mass loop order
    5   2                    # EWSB loop order
    6   2                    # beta-functions loop order
Block SPhenoInput            # SPheno specific input
    1  -1                    # error level
    2   1                    # SPA conventions
    11  0                    # calculate branching ratios
    13  0                    # include 3-Body decays
    12  1.000E-04            # write only branching ratios larger than this value
    31  -1                   # fixed GUT scale (-1: dynamical GUT scale)
    32  0                    # Strict unification
    34  1.000E-04            # Precision of mass calculation
    35  40                   # Maximal number of iterations
    37  1                    # Set Yukawa scheme
    38  2                    # 1- or 2-Loop RGEs
    50  1                    # Majorana phases: use only positive masses
    51  0                    # Write Output in CKM basis
    52  0                    # Write spectrum in case of tachyonic states
    55  1                    # Calculate one loop masses
    57  0                    # Calculate low energy constraints
    60  0                    # Include possible, kinetic mixing
    65  1                    # Solution tadpole equation
    75  0                    # Write WHIZARD files
    76  0                    # Write HiggsBounds file
    86  0.                   # Maximal width to be counted as invisible in Higgs decays
    510 0.                   # Write tree level values for tadpole solutions
    515 0                    # Write parameter values at GUT scale
    520 0.                   # Write effective Higgs couplings (HiggsBounds blocks)
    525 0.                   # Write loop contributions to diphoton decay of Higgs
Block MINPAR
    1   [50..1000]           # m0(MX)
    2   [50..1000]           # m12(MX)
    3   [1..100]             # tan(beta)(MZ) DRbar
    4   {-1,+1}              # sign(mu)
    5   [-1000..1000]        # A0(MX)
\end{lstlisting}
